MS_data_clean

### 2022-07-21 Fowler-GLOBI Modeling/GLOBI-Fowler Data Prep.Rmd
changing path names

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lifecycle)
library(rvest)
library(dplyr)
library(plotly)
library(dplyr)
library(data.table)

@@

```{r, echo = False}
options(max.print=1000000)
interactions_b <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/interactions_dup.csv') %>% dplyr::select(-X)

@@

write.csv(table_test, 'fowler')
```

@@

write.csv(plotdf, 'BeeCiteRaw')
```

@@

write.csv(plotdf, 'BeeCiteC5')
```

@@

write.csv(plotdf, 'BeeCiteW')
```

@@

write.csv(plotdf, 'BeeCiteRawGenus')
```

@@

write.csv(plotdf, 'BeeCiteC5Genus')
```

@@

write.csv(plotdf, 'BeeCiteWGenus')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/colleen/Dropbox/Fall_2014/ucsb/Bee-Specialization-Modeling/")
knitr::opts_knit$set(error=T)

library(lifecycle)
library(rvest)
library(dplyr)
library(plotly)
library(tidyverse)
library(data.table)

@@

```{r, echo = False}
options(max.print=1000000)
interactions_b <- read.csv('modeling_data/interactions_dup.csv')

@@

write_csv(table_test, 'modeling_data/fowler')
```

@@

write_csv(plotdf, 'modeling_data/BeeCiteRaw')
```

@@

write_csv(plotdf, 'modeling_data/BeeCiteC5')
```

@@

write_csv(plotdf, 'modeling_data/BeeCiteW')
```

@@

write_csv(plotdf, 'modeling_data/BeeCiteRawGenus')
```

@@

write_csv(plotdf, 'modeling_data/BeeCiteC5Genus')
```

@@

write_csv(plotdf, 'modeling_data/BeeCiteWGenus')
```

### 2022-07-21 MS_data_modeling/MS_data_explore.Rmd
changing path names

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lifecycle)
library(rvest)
library(dplyr)
library(tidyr)
library(plotly)
library(dplyr)
library(data.table)
library(stringr)
library(readxl)
library(kableExtra)
library(rcol)
library(plyr)
library(caret)

MS_data <- readxl::read_xlsx('/Users/nickbachelder/Desktop/UCSB Archive/Fall 2021/Data for Bees/DATA_pollen-diet-breadth_list_12-5-21_ALR.xlsx', sheet = 2)

globee <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Fowler-GLOBI Modeling/BeeCiteRaw') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_5cut <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Fowler-GLOBI Modeling/BeeCiteC5') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_T <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Fowler-GLOBI Modeling/BeeCiteW') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

fowler <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Fowler-GLOBI Modeling/fowler') %>%
   mutate(interestBee = str_to_title(interestBee)) %>%
  dplyr::select(interestBee, west_specialist, east_specialist, cent_specialist, specialist, Status_E, Status_W, Status_C) %>% 
  filter(grepl('^\\w+\\s\\w+$', interestBee))

globeeGenus <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Fowler-GLOBI Modeling/BeeCiteRawGenus') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_5cutGenus <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Fowler-GLOBI Modeling/BeeCiteC5Genus') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_TGenus <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Fowler-GLOBI Modeling/BeeCiteWGenus') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)
```

```{r}
interactions <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/interactions_dup.csv')

@@

write.csv(avery_send, "/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Family_Level_Transform.csv")

@@

final

write.csv(final, '/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/modeling_data/visitation_specialization_df')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/colleen/Dropbox/Fall_2014/ucsb/Bee-Specialization-Modeling/")
knitr::opts_knit$set(error=T)

library(lifecycle)
library(rvest)
library(tidyverse)
library(plotly)
library(data.table)
library(stringr)
library(readxl)
library(kableExtra)
library(rcol)
library(plyr)
library(caret)
```

```{r}
getwd()

MS_data <- readxl::read_xlsx('modeling_data/DATA_pollen-diet-breadth_list_12-5-21_ALR.xlsx', sheet = 2)

globee <- read_csv('modeling_data/BeeCiteRaw') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_5cut <- read_csv('modeling_data/BeeCiteC5') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_T <- read_csv('modeling_data/BeeCiteW') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

fowler <- read.csv('modeling_data/fowler') %>%
   mutate(interestBee = str_to_title(interestBee)) %>%
  dplyr::select(interestBee, west_specialist, east_specialist, cent_specialist, specialist, Status_E, Status_W, Status_C) %>% 
  filter(grepl('^\\w+\\s\\w+$', interestBee))

globeeGenus <- read_csv('modeling_data/BeeCiteRawGenus') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_5cutGenus <- read_csv('modeling_data/BeeCiteC5Genus') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)

globee_TGenus <- read_csv('modeling_data/BeeCiteWGenus') %>%
  dplyr::select(-west_specialist, -east_specialist, -cent_specialist, -specialist)
```

```{r}
interactions <- read_csv('modeling_data/interactions_dup.csv')

@@

# write.csv(avery_send, "/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/Family_Level_Transform.csv")

@@

final
write_csv(compare_df,'modeling_data/compare_df.csv')
write_csv(final, 'modeling_data/visitation_specialization_df')
```
